Eclipse Che for Fair and Easy Education

### 2019-06-12 che.tex
Addition to future work

\documentclass[utf8]{lni}

@@

\subsection{Vulnerability}
The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
Dependent on the setup, the attacker could also auto-deploy hidden spyware into a production environment. 
While this is also a problem for normal developer teams, the fast pace of deployments with Che requires additional care. 
A rich CI/CD environment, such as a well-maintained Jenkins may lead to less-detailed code-reviews, as both unit- and end-to-end-tests succeed.  
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.

@@

While this sounds harsh towards companies, unbiased education for students is not a nice thing to have, but a core concept of education in general. 
Only if that is true, the students can make unbiased decisions and make unbiased research. 
Being dependent on Google for Universities is in a similar way disturbing, as if a biology faculty would be sponsored by Bayer. 
One can only imagine a grim future if the curriculum is influenced by profit. 
\section*{Future Work}
\label{sec:FutureWork}
As this paper only summarizes benefits and outlines some ideas, the next step would be to put it to the test.
In addition, a study could be elaborated on both the acceptance and effect of a CI/CD based development course with Che. 
Unfortunately, the study would lack any comparison as there are few courses on this topic. 
These studies could be done with universities and corporations, which 
may yield very different results.

>>>>

\documentclass[english,utf8]{lni}

@@

\subsection{Vulnerability}
The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.

@@

While this sounds harsh towards companies, unbiased education for students is not a nice thing to have, but a core concept of education in general. 
Only if that is true, the students can make unbiased decisions and make unbiased research. 
Being dependent on Google for Universities is in a similar way disturbing, as if a biology faculty would be sponsored by Bayer. 
One can only imagine a grim future if the curriculum is influenced by profit. 
\section*{Future Work}
\label{sec:FutureWork}
As this paper only argues about the possible improvement of education using Che, it should be therefore tested. 
A study could be hold on both the acceptance and effect of a CI/CD based development course with Che in comparison to a conventional course. 
These studies could be done with universities and corporations, which 
may yield very different results.

Additionally, it should be inspected whether the studies on general motivation and education hold for IT-students.

When moving the scope from student to educator, a study can be hold about the time spent of the teacher on which part of the course and whether a positive effect on effective feedback-time can be achieved.
